handover

### 2021-01-29 inst/handover.Rmd
typo
aylmer package not needed (it is deprecated anyway)

Thus we see that in 26 cases, both reviewers answered "yes", in 18
<both said "no".  The table also records partial responses that include
observations missed by one or both reviewers.  Responses missed by
both reviewers are uninformative and automatically rejected:
structural zeros, in `aylmer` terminology.  We first apply the Aylmer
test to assess whether the two reviewers give the same proportion of
"yes" responses:

@@

```{r,samplepsi,message=FALSE,cache=TRUE}
jj <- rp(300000,H=handover)
head(jj)
psifun <- function(x){x[3]/(x[2]+x[3])}
logoddsfun <- function(x){log(x[2]/x[3])}
psi <- apply(jj,1,psifun)
log_odds <- apply(jj,1,logoddsfun)
psi_complete <- rbeta(length(psi),2,6)
```

>>>>

Thus we see that in 26 cases, both reviewers answered "yes", and in 18
both said "no".  The table also records partial responses that include
observations missed by one or both reviewers.  Responses missed by
both reviewers are uninformative and automatically rejected:
structural zeros, in `aylmer` terminology.  We first apply the Aylmer
test to assess whether the two reviewers give the same proportion of
"yes" responses:

@@

```{r,samplepsi,message=FALSE,cache=TRUE}
jj <- rp(3000,H=handover)
head(jj)
psifun <- function(x){x[3]/(x[2]+x[3])}
logoddsfun <- function(x){log(x[2]/x[3])}
psi <- apply(jj,1,psifun)
log_odds <- apply(jj,1,logoddsfun)
psi_complete <- rbeta(length(psi),2,6)
```
